%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

% --- THIS IS THE NEW COMMAND TO FIX YOUR ERROR ---
\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}
% ------------------------------------------------

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADER----------
\begin{center}
    \textbf{\Huge \scshape Timothy Micheletto} \\ \vspace{1pt}
    Staff MLOps Engineer $|$ Engineering Leader \\ \vspace{1pt}
    \small 0434 799 667 $|$ \href{mailto:tim.micheletto@gmail.com}{\underline{tim.micheletto@gmail.com}} $|$
    \href{https://linkedin.com/in/timmicheletto}{\underline{linkedin.com/in/timmicheletto}} $|$
    Melbourne, Australia
\end{center}


%-----------SUMMARY-----------
\section{Professional Summary}
  \small{Engineering leader and Staff Engineer with 20+ years of experience designing distributed systems at scale. Specialized in bridging the gap between Applied Science and Product Engineering to ship TB-scale inference pipelines and GenAI products. Proven track record of driving architectural strategy and shipping velocity, bringing a rigorous software engineering mindset to the challenges of scaling ML in production.}


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Go (Golang), TypeScript/NodeJS, SQL, Scala, C\#} \\
     \textbf{MLOps \& Data}{: Dask, Prefect, TensorFlow, RAG, Batch Inference, Model Observability, Snowflake, Postgres, DynamoDB} \\
     \textbf{Cloud \& Platform}{: AWS (EKS, ECS, Lambda, Kinesis), Kubernetes, Terraform, Docker, FastAPI, Event-Driven Architecture}
    }}
 \end{itemize}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    % XERO (Grouped)
    \resumeSubheading
      {Xero}{Melbourne, Australia}
      {Senior Engineer - Machine Learning (Research Team)}{Sep 2024 -- Sep 2025}
      \resumeItemListStart
        \resumeItem{Architected a \textbf{specialist model orchestrator} to maximize precision, implementing logic to dynamically select optimal predictions from an ensemble of specialist models.}
        \resumeItem{Engineered \textbf{TB-scale distributed data pipelines} utilizing \textbf{Dask} and Python to perform batch inference on multi-terabyte datasets, establishing the foundational framework for offline model evaluation.}
        \resumeItem{Core contributor to the engineering delivery of \textbf{JAX (Just Ask Xero)}, a headline GenAI feature announced at XeroCon 2025, specifically focusing on the automated bank reconciliation model.}
        \resumeItem{Established reproducible data foundations by building automated pipelines to generate training/validation datasets from OLTP sources, significantly accelerating experimentation cycles for Applied Scientists.}
      \resumeItemListEnd

    \resumeSubSubheading
      {Engineering Manager - Machine Learning}{Sep 2023 -- Sep 2024}
      \resumeItemListStart
        \resumeItem{Led the end-to-end engineering delivery of Xero’s first \textbf{GenAI product} (RAG-based customer support agent), coordinating cross-functional alignment between Applied Science and Customer Experience teams.}
        \resumeItem{Designed and executed the organizational restructuring of a 14-engineer team into 3 domain-aligned pods, resulting in optimized delivery velocity and reduced communication overhead.}
        \resumeItem{Managed 9 direct reports---personally recruiting 3---and designed the department-wide interview loop to establish rigorous standards for MLOps competencies.}
        \resumeItem{Championed the unified \textbf{Batch Inference Platform} initiative, standardizing architectural patterns for all batch AI products to eliminate fragmentation and reduce technical debt.}
        \resumeItem{Directed the technical implementation of GDPR "Right to be Forgotten" workflows across distributed data stores, ensuring compliance without disrupting production availability.}
      \resumeItemListEnd

    \resumeSubSubheading
      {Staff Engineer - Data Applications}{Mar 2022 -- Sep 2023}
      \resumeItemListStart
        \resumeItem{Architected and led the implementation of the Cash flow Understanding and Prediction Service (CUPS) utilizing \textbf{Prefect} for orchestration; led the project from inception to General Availability (GA).}
        \resumeItem{Designed distributed batch inference pipelines processing terabytes of data daily, generating cash flow predictions for the entire Xero customer base.}
        \resumeItem{Standardized \textbf{Terraform} patterns for IAM Roles, significantly reducing infrastructure provisioning time for new ML services.}
        \resumeItem{Built high-throughput, low-latency APIs (\textbf{FastAPI/AWS EKS/DynamoDB}) to serve predictions to millions of customers.}
        \resumeItem{Defined and implemented SLIs/SLOs for ML services to ensure high availability and enable proactive, data-driven incident response.}
      \resumeItemListEnd

    \resumeSubSubheading
      {Senior Engineer - Data Applications}{May 2021 -- Mar 2022}
      \resumeItemListStart
        \resumeItem{Accelerated the deployment of heuristic cash flow models by building automated CI/CD pipelines for Python packages, reducing deployment friction between Science and Engineering.}
      \resumeItemListEnd

    % LATITUDE
    \resumeSubheading
      {Latitude Financial Services}{Melbourne, Australia}
      {Lead Software Engineer}{Apr 2020 -- May 2021}
      \resumeItemListStart
        \resumeItem{Spearheaded the architectural transformation of the Identity Platform (\textbf{Okta/Golang}), enabling Single Sign-On (SSO) for millions of customers.}
        \resumeItem{Executed the migration of legacy user bases from AWS Cognito to Okta with zero downtime.}
        \resumeItem{Acted as Technical Product Manager for a platform team of 4 engineers, defining roadmap requirements and driving execution.}
      \resumeItemListEnd

    % SEEK (Grouped)
    \resumeSubheading
      {SEEK}{Melbourne, Australia}
      {Principal Software Developer}{Jul 2018 -- Mar 2020}
      \resumeItemListStart
        \resumeItem{Selected for a high-priority "Tiger Team" to decompose legacy monoliths into modern cloud-native microservices (\textbf{AWS ECS/TypeScript/DynamoDB}) using the \textbf{Strangler Fig pattern}.}
        \resumeItem{Led the implementation of a Resume Parsing pipeline (Scala) and a serverless Profile Nudge System (AWS Lambda) to interactively capture missing profile attributes and enrich the candidate data graph.}
      \resumeItemListEnd

    \resumeSubSubheading
      {Senior Software Developer}{Mar 2016 -- Jul 2018}
      \resumeItemListStart
        \resumeItem{Developed event-driven microservices (NodeJS/AWS SNS/SQS) to power real-time candidate feedback loops.}
        \resumeItem{Integrated complex variable pricing logic into high-traffic C\# ASP.NET monoliths.}
      \resumeItemListEnd

    % LEICA
    \resumeSubheading
      {Leica Biosystems}{Melbourne, Australia}
      {Senior Software Engineer}{May 2013 -- Mar 2016}
      \resumeItemListStart
        \resumeItem{Developed IoT-style monitoring dashboards for pathology laboratory equipment using AngularJS and C\#.}
        \resumeItem{Built the Inventory Manager application to optimize consumable reordering for lab supervisors.}
      \resumeItemListEnd

    % EARLY CAREER
    \resumeSubheading
      {Early Career}{2003 -- 2012}
      {Various Roles: Integration Consultant, Lead Developer, Graduate}{UK \& Australia}
      \resumeItemListStart
        \resumeItem{Enterprise Integration Consultant | Various Contracts (UK) (2008 -- 2012)}
        \resumeItem{Lead Integration Developer | Linfox (2007 -- 2008)}
        \resumeItem{Consultant / Graduate | Oakton / Downer (2003 -- 2006)}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------EDUCATION & CERTIFICATIONS-----------
\section{Education \& Certifications}
  \resumeSubHeadingListStart
    \resumeSubheading
      {RMIT University}{Melbourne, Australia}
      {Bachelor of Engineering (Computer Systems)}{2000 -- 2002}

    \vspace{2pt}
    \item \textbf{Certifications}:
    \small{
      DeepLearning.AI: Agentic AI (Nov 2025) $|$ Stanford University Online: Machine Learning Specialization (Oct 2025)
    }
  \resumeSubHeadingListEnd


%-----------INTERESTS-----------
\section{Interests}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Surfing, Motorcycles, Crossfit, Machine Learning, Data Engineering
    }}
 \end{itemize}

\end{document}
